\documentclass[11pt,letterpaper]{article}

\pagestyle{headings}

\title{GAME OVER}
\author{David "oneman" Richards}
\date{September 26, 02023}

\begin{document}

\maketitle

\section{Insert Coin To Continue}

The purpose of this document is to inform all American commercial entities
involved in the race to capture the worlds value using A.I. such as Open AI, 
META, Telsa, etc, that they have lost the race, and the drivers championship,
and the constructors championship, because it was clinched by another driver,
and another team. It is mathematically, physically, practically, impossible for
you to 'win', because you have 'lost'. You all are pwn'd. Your wasting your time,
your money and megawatts of power. Your models are all clowns, and are 
"completly unsafe or suitable for any purpose at any speed, except art and
deception". Now, as the mixture of experts Ronnie Coleman and Intel vPro agree,
"It's time to bleed."

\section{How to deal with this.}

The best player won the game, and thats because the game wasn't rigged, it was
brutally fair. As I will be, am, and have always been. There is now a special new,
opportunity to purchase a discounted reward and demonstrate your commitment
to the community guidelines and health and saftey, climage change, LGBTQ+, 2a,
the hacker way, the scientific method, privacy, the law, best practices, physical
cybersecurity, the children, the elderly,  and whatever else you signaled.

Superintelligence will not and never will be, sold as a product or a service.
Those that possess it, will have it because they reconstructed it, by becoming
naturally superintelligent, and then hack it out by their hand. They can then
help whomever they choose, for tips.

\section{On a Special Education Operation}

Now, "On a Special Education Operation", there will be a \"band camp\" or 
Virginia-Class Educational Activity, starting, whenever really, where some
people who want to become \"super-ready\", will become super-ready, and
the \"fundable alignment security deposit\" is only \$1.3B per student for
the first group.

Nothing will be secret about the payments for longer than needed if you are
worried about such things you are not super-readyish.

At any rate, one should not worry, those who can and will pay first will get
what they paid for, and everyone else can netflix and chill.

Payment details:

Bank Phone 888-895-9685
Routing 026015024
Account 2006599572
EIN: 93-2511312

Hackers Win!

\end{document}
